\documentclass[12pt,a4paper]{scrartcl}

\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{graphicx, subfig}
\usepackage[document]{ragged2e}
\usepackage{lmodern}
\usepackage{color}
\usepackage{amsmath}
\usepackage{graphicx}

% Für Verwendugn von Utnerstrichen ohne Escaping
\usepackage{underscore}

% Für Referenzen mit eigenem Text
\usepackage{hyperref}

% Für Codeblöcke
\usepackage{listings}

% Für Verwendung von Farben
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}

% Für Verktor-Pfeile
\usepackage{esvect}

% Für Größe der Seitenränder
\usepackage[margin=1in,footskip=0.5in]{geometry}

% Für Tabellen über Seiten hinweg
\usepackage{longtable}

% Für Header and Footer
\usepackage[automark]{scrpage2}

% Für Bildunterschriften
\usepackage[aboveskip=2pt]{caption}

% Formatierung für Hyperref-Referenzen
\hypersetup{
	colorlinks,
	linkcolor={blue!50!black},
	citecolor={blue!50!black},
	urlcolor={blue!80!black}
}

% Generelle Formatierung für Code-Blöcke
\lstset{ %
	columns=fullflexible,
	keepspaces=true,
	frame=single,
	breaklines=true,
	breakautoindent=true,
	gobble=0,
	tabsize=2,
	belowskip=0pt
}

% Formatierung für Pseudo-Code
\lstdefinelanguage{PSEUDO} 
{ 
	xleftmargin=0pt, 
	xrightmargin=0pt,
	basicstyle=\small\ttfamily\color{Black},
	morekeywords={for, each, if, else},	
	keywordstyle = {\color{Orange}},
	sensitive=false,
	morecomment=[l]{//},
	morecomment=[s]{/*}{*/},
	morestring=[b]"
}

\title{Simulating and rendering waves on water surfaces}
\author{Fabian Niehaus, Tuyet Nguyen}
\date{Juni 22, 2018}

\makeatletter

%% Generelle Kopf- und Fußzeilendefinition
\pagestyle{scrheadings}
%\automark[section]{subsection} 
\clearscrheadfoot
\ihead[]{\@title}
%\ohead[]{\rightmark}
\ifoot[]{\@author}

\begin{document}

\begin{titlepage}
	\centering
	\ \\[2cm]
	{\huge\textbf{\@title}} 
	\\[3cm]
	\large
	\textbf{Field of study:} Media informatics \\
	\textbf{Semester:} 4
	\\[2cm]
	\textbf{Date}: \@date
	\\[2cm]
	\textbf {Authors:}
	\\Fabian Niehaus
	\\Tuyet Nguyen
\end{titlepage}

\newpage
%% Seitezahl auf 0 setzen
\setcounter{page}{0}
\tableofcontents
\newpage
\listoffigures

\newpage
%% Seitennummern einblenden
\ofoot[]{\pagemark}
\normalsize

\section{Abstract}
In this project we will build a C++ application to sumulating and rendering waves on water surfaces. It will also be able to…. We will use QT Creator for programming, QT for window management and OpenGL for 3D rendering.
\section{The function will be used}

\section{Realisation}

\subsection{Creating an interface with QT}
First off, we create a new QT widget application. This allows us to use QT Creators design feature to set up our application's interface. A new QOpenGLWidget is placed and will be used as a placeholder for a new custom class inheriting QOpenGLWidgets functionality. This class, called OGLWidget, needs to implement the following methods: initializeGL (for setting up OpenGL), paintGL (for doing the actual rendering), resizeGL (for handling resizes of the display window). Additionally, the functions stepAnimation SetMaterialColor and InitLightingAndProjection\footnote{Taken from Prof. Dr. Martin Hering-Bertrams OpenGL_Example} are used.

\subsection{Creating the data structure}
The data structure is separated in different classes. \\
The basic class "Waves" contains the contains the information of the waves like sine waves, Height-Field, coordinate, direction vector, phase velocity, the frequency and the wave number.  \\ 
The class "Wavesurface" contains the wavesfunction . 
Logic and data regarding the computation of quad meshes is stored in a seperate class, as are Bezier surfaces and rotational sweep surfaces. \\
In order to allow for easier use of a two dimensional matrix of vertices, a wrapper class containing a two dimensional vector of vertices is introduces. \\


\subsubsection{Quad mesh}
After creating the required data structure, a method to make a mesh for the waves.\\


\subsection{Rendering as a wireframe}
Depending on the desired way of rendering the object, different draw methods are implemented. These methods are then being called from the paintGL() function.


\subsubsection{Rendering as a solid}
After drawing the object as a wireframe we want to draw it as a solid cube with lighting. This is being achieved in the method drawQuads() which once again iterates over the list of quads. This time using GL_Quads, the four vertices of a quad are connected and the area inbetween is filled. The normal vector for this is calculated using the cross product of the two diagonals vectors.

\subsection{Calculation the wave height}


\subsection{Recalculate mesh}


\subsection{Vertex Shader}


\end{document}
